Meta-analysis

### 2019-10-23 05_MetaAnalysis.Rmd
install packages Started work on First incidence graph

```{r MEsummary_Libraries, message=FALSE}
library(tidyverse)
library(theme.usq)
library(bomrang)
source("R/import_data.R")
```

@@

>>>>

```{r MEsummary_Libraries, message=FALSE}
install.packages("tidyverse")
install.packages("devtools")
devtools::install_github("https://github.com/PaulMelloy/bomrang")
devtools::install_github("https://github.com/adamhsparks/theme.usq")

library(tidyverse)
library(theme.usq)
library(bomrang)
source("R/import_data.R")
```

@@

```{r first_incidence}
# Here I want to build a plot of horizontal lines indicating the season length and
# place a dot on the line to indicating the day of the year first sign was observed for that trial

FS_dates <- data.frame(first_sign = as.Date(unique(PM_MB_means$first_sign_disease)),
                       plant.date = as.Date(PM_MB_)
)

PM_MB_

dat1 <- data.frame(First_sign = sort(format(FS_dates, "%b-%d"))[c(5:25,1:4)])

dat1$First_sign <- as.Date(dat1$First_sign)

ggplot(dat1, aes(x = First_sign))+
   geom_dotplot()+
   scale_x_date()+
   coord_flip()

as.character(format(FS_dates, "%b-%d"))

as.Date()
